---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggformula)
library(R2jags)
library(CalvinBayes)
```
# CalvinBayes

The goal of CalvinBayes is to collect up some data sets and utilities for 
learning/teaching Bayesian Data analysis.

## Installation

### Github

You can install the development version of CalvinBayes from GitHub with

``` r
devtools::install_github("rpruim/CalvinBayes")
```

### CRAN

This package is not on CRAN.

<!-- You can install the released version of CalvinBayes from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("CalvinBayes") -->
<!-- ``` -->

## Example

Here is an example that demonstrates the use of the `posterior()` function to extract 
isamples from the posterior distribution of an object fit using the R2jags package.

```{r example-1a}
library(R2jags)
library(CalvinBayes)
data("z15N50")
glimpse(z15N50)
```

```{r example-1b}
# describe the model
bern_model <- function() {
  for (i in 1:N) {
    # each response is Bernoulli with fixed parameter theta
    y[i] ~ dbern(theta)  
  }
  theta ~ dbeta(1, 1)    # prior for theta
}
```

```{r example-1c}
# Fit the model
bern_jags <- 
  jags(
    data = list(y = z15N50$y, N = nrow(z15N50)),
    model.file = bern_model,
    parameters.to.save = c("theta")
  )
```

```{r example-1d}
glimpse(posterior(bern_jags))
library(ggformula)
gf_density(~ theta, data = posterior(bern_jags))
```
